\documentclass[11pt,a4paper,sans]{moderncv}   % possible options include font size ('10pt', '11pt' and '12pt'), 
    % paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 
    %'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv 主题
\moderncvstyle{classic}                        % 选项参数是 ‘casual’, ‘classic’, ‘oldstyle’ 和 ’banking’
\moderncvcolor{purple}                        % 选项参数是 ‘blue’ (默认)、‘orange’、‘green’、‘red’、‘purple’ 和 ‘grey’
%\nopagenumbers{}                             % 消除注释以取消自动页码生成功能

% 字符编码
\usepackage[utf8]{inputenc}                   % 替换你正在使用的编码
%\usepackage{CJKutf8}

% 调整页面
\usepackage[scale=0.88]{geometry}
\setlength{\hintscolumnwidth}{2.0cm}           % 如果你希望改变日期栏的宽度

% hyperlinks
% \usepackage{hyperref}

% 个人信息
\firstname{\qquad Chen}
\familyname{Zhu}
\address{New York, NY, 10022}
\phone{Mobile: 917-684-1583} 
\email{Email: xzzhuchen@gmail.com}
% 可选项、如不需要可删除本行
% \homepage{chenzhu.github.io}                  % 可选项、如不需要可删除本行

%----------------------------------------------------------------------------------
%            内容
%----------------------------------------------------------------------------------

\begin{document}
%\begin{CJK}{UTF8}{gbsn}                       % 详情参阅CJK文件包
\maketitle

\section{Technology Skills}
\cventry{Web}{JavaScript(Proficient), AngularJS, NodeJS, AJAX, HTML, CSS}{}{}{}{}
\cventry{Programming}{Java(Proficient), Python, Linux Shell, SQL}{}{}{}{}
\cventry{Tools \& IDE}{JIRA, Git, VS Code, Eclipse, Virtual Box, Sublime, Vim}{}{}{}{}


\section{Work Experience}
\renewcommand{\baselinestretch}{1.25}

% \cventry{Jun.2014 - Sep.2014}
% {Web Developer Intern}
% {TMC Bonds}
% {Financial Industry}
% {New York}
% {
% 	{Coded trading report PDF generator by \textbf{NodeJS} and \textbf{Java} resulting quality improvement.}
% 	\newline
% 	{Learnt foundamental \textbf{Finance} principle that can assist working in a financial company.}
% 	\newline
% 	{Enhanced back-end server performance by more integrated build process.}
% 	\newline
% 	{Fixed front-end web application bugs timely.}
% }
\cventry{Apr.2019 - Present}
{Full Stack Developer}
{Intercontinental Exchange}
{Financial Industry}
{New York}
{
	{Investigating and research production issues provided quick and accurate resolutions.}
	\newline
	{Programming \textbf{Javascript} and Java projects meet deliverables quality.}
	\newline
	{Styling front-end web pages resulting in better user experience.}
	\newline
    {Participating spec design meetings to provide accurate estimations.}
    \newline
    {Mentoring new developers.}
}

\cventry{Jul.2017 - Apr.2019}
{Full Stack Developer}
{TMC Bonds}
{Financial Industry}
{New York}
{
	{Researched production issues resulting in strong support on client services.}
	\newline
	{Used \textbf{SDLC} tools such as Jira for high efficiency coding.}
	\newline
	{Styled front-end web pages for better user experience.}
	\newline
	{Joined project scope definition meetings to provide agile design on system.}
	\newline
	{Developped new market search result page with better data structure.}
}

\cventry{Jul.2015 - Jul.2017}
{Associate - Web Developer}
{TMC Bonds}
{Financial Industry}
{New York}
{
	{Programmed \textbf{ExtJs 6.0} front end projects learnt most of framework.}
	\newline
	{Used Linux command lines to conduct SDLC tasks.}
	\newline
	{Developped first Trade Blotter page with new design.}
}

\section{Project Experience}
\renewcommand{\baselinestretch}{1.25}

\cventry{Dec.2018 - Jun.2019}
{6.0 Post A Bid Wanted}
{Java, JavaScript, CSS}
{}{}
{
	{Upgraded trader's \textbf{Bid Wanted} creation system with ExtJS 6.0 library.}
	\newline
	{Debugged client-side web components with new Bid Wanted view and controller.}
	\newline
	{Refactored server side Bid Wanted services in Java.}
	\newline
	{Tested the Bid Wanted scenario ensured 90\% success rate.}
}

\cventry{Jan.2018 - Jul.2018}
{6.0 Fill Order Ticket}
{Java, JavaScript, CSS}
{}{}
{
	{Coded retail trader's fill order ticket using ExtJS 6.0 library.}
	\newline
	{Debugged on front-end code writting in \textbf{MVVC} framework.}
	\newline
	{Refactored edit ticket and fill ticket for integrated functionality.}
	\newline
	{Tested the fill order scenario ensured 90\% success rate.}
}

\cventry{Jan.2016 - Dec.2017}
{6.0 Order Ticket, IMS, 6.0 Institutional Trader Ticket}
{Javascript, Java}
{}{}
{
	{Learned internal TSA model in order to provide more accurate \textbf{data binding}.}
	\newline
	{Coded components such as clearing and settlement panel, buy as user panel and price change window.}
	\newline
	{Tested trader's work flow to ensure business behavior consistency.}
}

\cventry{Feb.2017 - Dec.2017}
{6.0 Market Search}
{JavaScript, Java}
{}{}
{
	{Implemented new user interface market snapshot page using ExtJS 6.0 library.}
	\newline
	{Teamed with other developers for better effective code.}
	\newline
	{Designed front-end column models using generic components.}
	\newline
	{Refactored back-end market search logic to more organized data structure.}
}

\cventry{Dec.2016 - Feb.2017}
{Ticket Report - Moody and MuniPoints Encryption API Update}
{Java, Javascript}
{}{}
{
	{Implemented encryption link generate system on server side.}
	\newline
	{Made web request on Java side to get encryption key calling Moody API.}
	\newline
	{Optimized UI to better allow user set credentials.}
}

\cventry{Sep.2016 - Nov.2016}
{6.0 Security Master Override}
{Javascript, Java}
{}{}
{
	{Designed user interface using MVVC framework.}
	\newline
	{Implemented the view, controller and view model with SM override new theme screen.}
	\newline
	{Maintained the back-end saving override service calls.}
}

\cventry{Dec.2015 - Jun.2016}
{6.0 Trade Blotter}
{Javascript, Java}
{}{}
{
	{Developed institutional trade detail ticket using ExtJS 6.0.}
	\newline
	{Establish store loading and data binding process on entire project.}
	\newline
	{Researched ExtJS data binding technique for cleaner code.}
}

\renewcommand{\baselinestretch}{1.25}

\cventry{Jul.2015 - Nov.2015}
{Security Master Screen}
{Javascript, Java}
{}{}
{
	{Designed a template for security master page.}
	\newline
	{Styled Security Master page to be fully screen and neat aligned.}
	\newline
	{Studied ExtJS 3.0 library.}
}

\renewcommand{\baselinestretch}{1.25}

\section{Education}
\cventry{Aug.2013 - May.2015}
{M.S. in Information Systems}
{Courant Institute of Mathematics, NYU}
{}{\textbf{GPA:3.75}}
{Courses: Algorithms, Social Multiplayer Games, Open Source Tools.}
\cventry{Sep.2009 - Jun.2013}
{B.S. in Management Information Systems}
{Renmin University of China}
{Beijing, China}
{}
{Courses: Java, Database, Knowledge Management.}

\closesection{}                   % needed to renewcommands
\renewcommand{\listitemsymbol}{-} % change the symbol for lists
%\clearpage\end{CJK}
\end{document}
